---
title: Dengue incidence cases in Sri Lanka from 2010 to 2017
author: Pushpakanthie Wijekoon
date: '2018-11-06'
categories:
  - R
tags:
  - R Markdown
slug: testing-a-new-post
image:
  caption: ''
  focal_point: ''
---

Dengue is a mosquito-borne viral infection caused by four dengue virus serotypes, and  disease caused mainly by Aedes aegypti and Aedes albopictus mosquitos. The Dengue virus is transmitted to humans through the bites of infected female mosquitoes, and Infected humans are the main carriers. The relevant mosquitos are daytime feeders,with peak biting periods early in the morning and in the evening before dusk.  

Dengue fever is endemic in Sri Lanka, and the Dengue incidence cases usually increases soon after the rainfall which is optimal for mosquito breeding.  The data for this study are obtained from the [Epidemiology Unit, Ministry of Health, Sri Lanka](http://www.epid.gov.lk/web/index.php?option=com_casesanddeaths&Itemid=448&lang=en).  



```{r echo=FALSE}
df=read.csv("dencolombo.csv")
df=df[,1:4]

```

The following interactive plots present the Dengue incidence cases for each district in Sri Lanka from year 2010 to 2017.
<br>

```{r denguecol, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Colombo District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```

<br>
 
```{r denguekan, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denkandy.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Kandy District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>
 
```{r denguegampaha, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("dengampaha.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Gampaha District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguegalle, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("dengalle.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Galle District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r dengueanupura, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denanupura.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Anuradhapura District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguebadulla, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denbadulla.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Badulla District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r dengueratnapura, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denratnapura.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Ratnapura District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r dengueampara, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denampara.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Ampara District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguebattica, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denbatticaloa.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Batticaloa District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguejaffna, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denjaffna.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Jaffna District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguekalmunai, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denkalmunai.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Kalmunai District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguekalutara, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denkalutara.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Kalutara District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguekegalle, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denkegalle.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Kegalle District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguekillinoch, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denkillinoch.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Killinochchi District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguekurunegala, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denkurunegala.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Kurunegala District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguemannar, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denmannar.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Mannar District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguematale, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denmatale.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Matale District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguematara, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denmatara.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Matara District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguemoneragala, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denmoneragala.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Maneragala District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguemulativu, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denmulativu.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Mulativu District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r dengueneliya, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denneliya.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Nuwaraeliya District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguepolonaru, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denpolonnaruwa.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Polonnaruwa District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r dengueputtalam, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denputtalam.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Puttalam District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguetrinco, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("dentrinco.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Trincomalee District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  

<br>

```{r denguevavuniya, echo=FALSE, message=FALSE, warning=FALSE}
df=read.csv("denvavuniya.csv")
df=df[,1:4]
library(dplyr)
library(plotly)
month <- c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec")
xform <- list(categoryorder = "array",
              categoryarray = c("Jan", "Feb", "Mar", "Apr","May", "Jun", "Jul", "Aug","Sep", "Oct", "Nov", "Dec"))
groupA <- df %>% filter(year == "2010")
groupB <- df %>% filter(year == "2011")
groupC <- df %>% filter(year == "2012")
groupD <- df %>% filter(year == "2013")
groupE <- df %>% filter(year == "2014")
groupF <- df %>% filter(year == "2015")
groupG <- df %>% filter(year == "2016")
groupH <- df %>% filter(year == "2017")
gBarChart <- data.frame(Month = names(table(groupA$month)),
                        countA = groupA$count,
                        countB = groupB$count,
                        countC = groupC$count,
                        countD = groupD$count,
                        countE = groupE$count,
                        countF = groupF$count,
                        countG = groupG$count,
                        countH = groupH$count)

p3 <- plot_ly(gBarChart,
              x = ~Month,
              y = ~countA,
              type = "bar",
              name = "2010") %>% 
  add_trace(y = ~countB,
            name = "2011") %>% 
  add_trace(y = ~countC,
            name = "2012") %>% 
  add_trace(y = ~countD,
            name = "2013") %>% 
  add_trace(y = ~countE,
            name = "2014") %>% 
  add_trace(y = ~countF,
            name = "2015") %>% 
  add_trace(y = ~countG,
            name = "2016") %>% 
  add_trace(y = ~countH,
            name = "2017") %>% 
  layout(title='Dengue incidence cases from year 2010 to 2017 in Vavuniya District', xaxis = xform, yaxis = list(title = "Dengue Count"),barmode = "group")
p3
```  



